---
title: "Final Exam"
author: "Fauzan Isnaini"
date: "4/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install packages and Import libraries

```{r}
#install.packages("rjson")
#install.packages("wordcloud")
#install.packages("RColorBrewer")
#install.packages("effsize")
#install.packages("rstatix")
```
```{r}
library(dplyr)
library("rjson")
library(tidyverse)
library(jsonlite)
library("textcat")
library("stringr")
library(wordcloud)
library(RColorBrewer)
library(tidytext)
library(effsize)
library(rstatix)
```

# 1. Telegram 2020

## Import cleaned data from Python 
```{r}
sentiment_telegram_2020 <- read_csv("telegram_2020_sentiment.csv")
sentiment_telegram_2020 <- sentiment_telegram_2020 %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_telegram_2020 %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_telegram_2020 <- sentiment_telegram_2020 %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_telegram_2020 %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))

```

# 2. Telegram 2021

## Import cleaned data from Python 
```{r}
sentiment_telegram_2021 <- read_csv("telegram_2021_sentiment.csv")
sentiment_telegram_2021 <- sentiment_telegram_2021 %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_telegram_2021 %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_telegram_2021 <- sentiment_telegram_2021 %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_telegram_2021 %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))

```

# 3. Whatsapp 2020

## Import cleaned data from Python 
```{r}
sentiment_whatsapp_2020 <- read_csv("whatsapp_2020_sentiment.csv")
sentiment_whatsapp_2020 <- sentiment_whatsapp_2020 %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_whatsapp_2020 %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_whatsapp_2020 <- sentiment_whatsapp_2020 %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_whatsapp_2020 %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))
```

# 4. Whatsapp 2021

## Import cleaned data from Python 
```{r}
sentiment_whatsapp_2021 <- read_csv("whatsapp_2021_sentiment.csv")
sentiment_whatsapp_2021 <- sentiment_whatsapp_2021 %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_whatsapp_2021 %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_whatsapp_2021 <- sentiment_whatsapp_2021 %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_whatsapp_2021 %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))

```

# 5. Telegram Feature

## Import cleaned data from Python 
```{r}
sentiment_telegram_feature <- read_csv("telegram_feature_sentiment.csv")
sentiment_telegram_feature <- sentiment_telegram_feature %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_telegram_feature %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_telegram_feature <- sentiment_telegram_feature %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_telegram_feature %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))
```


# 6. Whatsapp Feature

## Import cleaned data from Python 
```{r}
sentiment_whatsapp_feature <- read_csv("whatsapp_feature_sentiment.csv")
sentiment_whatsapp_feature <- sentiment_whatsapp_feature %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_whatsapp_feature %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_whatsapp_feature <- sentiment_whatsapp_feature %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_whatsapp_feature %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))
```


# 7. Telegram Privacy

## Import cleaned data from Python 
```{r}
sentiment_telegram_privacy <- read_csv("telegram_privacy_sentiment.csv")
sentiment_telegram_privacy <- sentiment_telegram_privacy %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_telegram_privacy %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_telegram_privacy <- sentiment_telegram_privacy %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_telegram_privacy %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))
```


# 8. Whatsapp Privacy

## Import cleaned data from Python 
```{r}
sentiment_whatsapp_privacy <- read_csv("whatsapp_privacy_sentiment.csv")
sentiment_whatsapp_privacy <- sentiment_whatsapp_privacy %>% mutate_all(funs(gsub("rt", "", .)))
```

## Generate wordcloud
```{r}
tweets_words <-  sentiment_whatsapp_privacy %>%
  select(tweets_cleaned) %>%
  unnest_tokens(word, tweets_cleaned)
words <- tweets_words %>% count(word, sort=TRUE)
set.seed(1234)
wordcloud(words = words$word, freq = words$n, min.freq = 1,max.words=200, random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```

## Descriptive Statistics
```{r}
sentiment_whatsapp_privacy <- sentiment_whatsapp_privacy %>% mutate(compound_sentiment = as.numeric(compound_sentiment))
sentiment_whatsapp_privacy %>% summarise(sentiment_mean = mean(compound_sentiment),
                                          sentiment_median = median(compound_sentiment),
                                          sentiment_min = min(compound_sentiment),
                                          sentiment_max = max(compound_sentiment),
                                          sentiment_sd = sd(compound_sentiment))
```


# Exploratory Analyses

## 1. Boxplot and Histogram of Whatsapp December 2020 VS Whatsapp January 2021

```{r}
sentiment_whatsapp_2020 <- sentiment_whatsapp_2020 %>% mutate(year="2020")
sentiment_whatsapp_2021 <- sentiment_whatsapp_2021 %>% mutate(year="2021")
whatsapp_2020_2021 <- bind_rows(sentiment_whatsapp_2020, sentiment_whatsapp_2021)
whatsapp_2020_2021 %>% ggplot(aes(x=year, y=compound_sentiment)) + geom_boxplot()
```

```{r}
ggplot(sentiment_whatsapp_2020, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

```{r}
ggplot(sentiment_whatsapp_2021, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

## 2. Boxplot and Histogram of Telegram December 2020 VS Telegram January 2021


```{r}
sentiment_telegram_2020 <- sentiment_telegram_2020 %>% mutate(year="2020")
sentiment_telegram_2021 <- sentiment_telegram_2021 %>% mutate(year="2021")
telegram_2020_2021 <- bind_rows(sentiment_telegram_2020, sentiment_telegram_2021)
telegram_2020_2021 %>% ggplot(aes(x=year, y=compound_sentiment)) + geom_boxplot()
```

```{r}
ggplot(sentiment_telegram_2020, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

```{r}
ggplot(sentiment_telegram_2021, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

## 3. Boxplot and Histogram of Whatsapp Privacy VS Telegram Privacy


```{r}
sentiment_whatsapp_privacy <- sentiment_whatsapp_privacy %>% mutate(apps="whatsapp")
sentiment_telegram_privacy <- sentiment_telegram_privacy %>% mutate(apps="telegram")
telegram_whatsapp_privacy <- bind_rows(sentiment_whatsapp_privacy, sentiment_telegram_privacy)
telegram_whatsapp_privacy %>% ggplot(aes(x=apps, y=compound_sentiment)) + geom_boxplot()
```


```{r}
ggplot(sentiment_whatsapp_privacy, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

```{r}
ggplot(sentiment_telegram_privacy, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

## 4. Boxplot and Histogram of Whatsapp Feature VS Telegram Feature

```{r}
sentiment_whatsapp_feature <- sentiment_whatsapp_feature %>% mutate(apps="whatsapp")
sentiment_telegram_feature <- sentiment_telegram_feature %>% mutate(apps="telegram")
telegram_whatsapp_feature <- bind_rows(sentiment_whatsapp_feature, sentiment_telegram_feature)
telegram_whatsapp_feature %>% ggplot(aes(x=apps, y=compound_sentiment)) + geom_boxplot()
```


```{r}
ggplot(sentiment_whatsapp_feature, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

```{r}
ggplot(sentiment_telegram_feature, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```


## 5. Boxplot and Histogram of Whatsapp VS Telegram (January 2021) 


```{r}
sentiment_telegram_2021 <- sentiment_telegram_2021 %>% mutate(apps="telegram")
sentiment_whatsapp_2021 <- sentiment_whatsapp_2021 %>% mutate(apps="whatsapp")
whatsapp_telegram <- bind_rows(sentiment_telegram_2021, sentiment_whatsapp_2021)
whatsapp_telegram %>% ggplot(aes(x=apps, y=compound_sentiment)) + geom_boxplot()
```


```{r}
ggplot(sentiment_whatsapp_2021, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```

```{r}
ggplot(sentiment_telegram_2021, aes(x=compound_sentiment)) + geom_histogram(binwidth=0.1)
```


# Inferential Statistics

## 1. Whatsapp 2021 VS Telegram 2021

```{r}
whatsapp = sentiment_whatsapp_2021 %>% pull(compound_sentiment)
telegram = sentiment_telegram_2021 %>% pull(compound_sentiment)
t.test(whatsapp, telegram, var.equal=T)
```
```{r}
whatsapp_telegram %>% cohens_d(compound_sentiment ~ apps, var.equal = FALSE)
```


## 2. Whatsapp Privacy VS Telegram Privacy


```{r}
whatsapp = sentiment_whatsapp_privacy %>% pull(compound_sentiment)
telegram = sentiment_telegram_privacy %>% pull(compound_sentiment)
t.test(whatsapp, telegram, var.equal=T)
```
```{r}
telegram_whatsapp_privacy %>% cohens_d(compound_sentiment ~ apps, var.equal = FALSE)
```


## 3. Whatsapp Feature vs Telegram Feature


```{r}
whatsapp = sentiment_whatsapp_feature %>% pull(compound_sentiment)
telegram = sentiment_telegram_feature %>% pull(compound_sentiment)
t.test(whatsapp, telegram, var.equal=T)
```
```{r}
telegram_whatsapp_feature %>% cohens_d(compound_sentiment ~ apps, var.equal = FALSE)
```

## 4. Whatsapp 2020 vs Whatsapp 2021


```{r}
wa_2020 = sentiment_whatsapp_2020 %>% pull(compound_sentiment)
wa_2021 = sentiment_whatsapp_2021 %>% pull(compound_sentiment)
t.test(wa_2020, wa_2021, var.equal=T)
```
```{r}
whatsapp_2020_2021 %>% cohens_d(compound_sentiment ~ year, var.equal = FALSE)
```

## 5. Telegram 2020 vs Telegram 2021


```{r}
tele_2020 = sentiment_telegram_2020 %>% pull(compound_sentiment)
tele_2021 = sentiment_telegram_2021 %>% pull(compound_sentiment)
t.test(tele_2020, tele_2021, var.equal=T)
```
```{r}
telegram_2020_2021 %>% cohens_d(compound_sentiment ~ year, var.equal = FALSE)
```
